```{r setup,echo=FALSE}
require(knitr)

opts_knit$set(root.dir = "C:/Users/wohlg_000/Documents/workspace/spectra-hash/utilities/evaluation/src/main/R")
```


---
title: "Index Evaluation"
author: "Gert Wohlgemuth"
date: "February 23, 2016"
output: html_document
---

Generated Report of the evaluation of the Index Calculations

```{r, echo=FALSE}

#install.packages("data.table")
library(data.table)
library(pander) 
library(plyr)

panderOptions('table.split.table', Inf) 

```


```{r, echo=FALSE}

#load data table
myData = read.table("result.txt",col.names = c('inchi','splash','index','count'))


```

Simple aggregated overview of the hit rates for the indexes.

```{r,echo=FALSE}
#aggregations

myDataTable = data.table(myData)
myData_agg_sum_index <- as.data.frame(myDataTable[, sum(count, na.rm = TRUE),by = list(index)])

```

```{r,echo=FALSE}


set.caption("aggregated sum for all indexes")
pander(arrange(myData_agg_sum_index,V1,decreasing=TRUE),justify = c('left', 'right'))

```

Simple aggregated overview of the hit rates, after normalizing based on the linear index

```{r}


myData_filtered_by_linear_index = as.matrix(subset(myData,grepl("Linear",index)))
normalized_data = myData

for(i in 1:nrow(myData_filtered_by_linear_index)){
    filtered = subset(normalized_data,splash == myData_filtered_by_linear_index[i,2])

        for(j in 1:nrow(filtered)){
        result = as.numeric(myData_filtered_by_linear_index[i,4])/as.numeric(normalized_data[j,4])        
        if(is.nan(result) || is.infinite(result)){
          result = 0
        }
        normalized_data[j,4] = result
  }
}


normalized_data_table = data.table(normalized_data)
normalized_data_agg_sum_index <- as.data.frame(normalized_data_table[, sum(count, na.rm = TRUE),by = list(index)])


```


```{r,echo=FALSE}

set.caption("aggregated summed score for all indexes")
pander(arrange(normalized_data_agg_sum_index,V1,decreasing=TRUE),justify = c('left', 'right'))
