```{r setup,echo=FALSE}
require(knitr)

opts_knit$set(root.dir = "C:/Users/wohlg_000/Documents/workspace/spectra-hash/utilities/evaluation/src/main/R")
```


---
title: "Index Evaluation"
author: "Gert Wohlgemuth"
date: "February 23, 2016"
output: html_document
---

Generated Report of the evaluation of the Index Calculations

```{r, echo=FALSE}

#install.packages("data.table")
library(data.table)
library(pander) 
library(plyr)

panderOptions('table.split.table', Inf) 

```


```{r, echo=FALSE}

#load data table
myData = read.table("result.txt",col.names = c('inchi','splash','index','count','duration','index_size'))

myData = myData[myData$count != 0,]

```

Simple aggregated overview of the hit rates for the indexes, higher is better

```{r,echo=FALSE}
#aggregations

myDataTable = data.table(myData)
myData_agg_sum_index <- as.data.frame(myDataTable[, sum(count, na.rm = TRUE),by = list(index)])

```

```{r,echo=FALSE}


set.caption("aggregated sum for all indexes")
pander(arrange(myData_agg_sum_index,V1,decreasing=TRUE),justify = c('left', 'right'))

```

Simple aggregated overview of the computational cost for the indexes. Cost is in ms, lower is better

```{r,echo=FALSE}
#aggregations

myDataTable = data.table(myData)
myData_agg_sum_index <- as.data.frame(myDataTable[, sum(duration, na.rm = TRUE),by = list(index)])

```

```{r,echo=FALSE}


set.caption("aggregated sum for all indexes")
pander(arrange(myData_agg_sum_index,V1,decreasing=TRUE),justify = c('left', 'right'))

```


Simple aggregated overview of the count/computational cost for the indexes. Higher is better

```{r,echo=FALSE}
#aggregations

myDataTable = data.table(myData)
myData_agg_sum_index <- as.data.frame(myDataTable[, sum((count+1)/(duration+1), na.rm = TRUE),by = list(index)])

```

```{r,echo=FALSE}


set.caption("aggregated sum for all indexes")
pander(arrange(myData_agg_sum_index,V1,decreasing=TRUE),justify = c('left', 'right'))

```

